\begin{paragraph}
    The document module exposes the basic commands that are designed to mimick the LaTeX main environment.
\end{paragraph}

\subsubsection{Implemented commands}
\begin{itemize}
    \item{\descriptor{global}{\command{title}{Title}}{Make a big fancy title.}}
    \item{\descriptor{global}{\command{section}{Title}}{Make a section title.}}
    \item{\descriptor{global}{\command{subsection}{Title}}{Make a subsection title.}}
    \item{\descriptor{global}{\command{subsubsection}{Title}}{Make a subsubsection title.}}
    \item{\descriptor{global}{\command{textbf}{Text}}{Render Text in \textbf{bold}.}}
    \item{\descriptor{global}{\command{textit}{Text}}{Render Text in \textit{italics}.}}
    \item{\descriptor{global}{\command{underline}{Text}}{Render Text \underline{underlined}.}}
    \item{\descriptor{global}{\command{hline}}{Make a horizontal line.}}
    \item{\descriptor{global}{\command{newline}}{Line break, equivalent to a double backslash.}}
    \item{\descriptor{global}{\command{paragraph}{text}}{Render the text as a paragraph, normally not noticable, but might have implications if a stylesheet is loaded. Use for a single line of text without commands only, please use the environment \textit{paragraph} otherwise.}}
    \item{\descriptor{global}{\command{ref}{label}}{Reference a label (from an image, for example). Works with both forward and backwards declaration (The label can be both above and below the ref command). Outputs a question mark when the label is undefined.}}
    \item{\descriptor{global}{\command{define}{Variable}{Value}}{Set the global Variable to Value. Often used to change module behaviour.}}
    \item{\descriptor{global}{\command{href}{URL}{Text}}{Make a hyperlink to URL with text Text}
\end{itemize}

\subsubsection{Special characters}
MarTeX has some special characters you need to escape to render:
\begin{tabular}{|l | l |}
\hline
\textbf{Command}  &  \textbf{Result} \\
\hline \hline
\command{,}	     & Small non-breaking space} \\
\command{\&}     & \& \\
\command{\%}	 & \% \\
\command{\$}   	 & \$ \\
\command{copy}	 & \copy \\
\command{\>}	 & \> \\
\command{\<}	 & \< \\
\command{\}}	 & \} \\
\command{\{}	 & \{ \\
\command{cdot}	 & \cdot \\
\command{pm}	 & \pm \\
\command{euro}	 & \euro \\
\command{pound}	 & \pound \\
\command{tm}	 & \tm \\
\command{deg}	 & \deg \\
\command{"}AaEeIiOoUuy & \"A\"a\"E\"e\"I\"i\"O\"o\"U\"u\"y \\
\command{'}AaEeIiOoUuZ & \'A\'a\'E\'e\'I\'i\'O\'o\'U\'u\'Z \\
\command{`}AaEeIiOoUu & \`A\`a\`E\`e\`I\`i\`O\`o\`U\`u \\
\command{^}AaEeIiOoUu & \^A\^a\^E\^e\^I\^i\^O\^o\^U\^u \\
\command{~}AaIiOoNnUu & \~A\~a\~I\~i\~O\~o\~N\~n\~U\~u \\
\command{.}AaUu & \.A\.a\.U\.u \\
\command{-O}\command{-o} & \-O\-o \\
\command{ss} & \ss \\
\command{Alpha}\command{alpha} & \Alpha\alpha \\
\command{Beta}\command{beta} & \Beta\beta \\
... & ... \\
\command{Phi}\command{phi} & \Phi\phi \\
\command{Omega}\command{omega} & \Omega\omega \\
\command{backslash} & \backslash \\
\hline
\end{tabular}

\subsubsection{Implemented environments}
\paragraph{In MarTeX an environment is defined as the area between a begin and matching end command:}
\begin{code}{latex}
\begin{verbatim}
\begin{Environment} 
    Environment content
\end{Environment}
\end{verbatim} 
\end{code}

\begin{itemize}
    \item{\envdescriptor{document}{Does basically nothing right now, but might do in the future. For now it is there for the TeX code-style idea.}}
    \item{\envdescriptor{paragraph}{Does the same as the command 'paragraph', but now with begin and end commands. Works better for multiline paragraphs.}}
    \item{\envdescriptor{code}{Wrapper for the html 'pre' environment. Stuff in this environment is displayed with all whitespace intact (tabs, newlines, etc)}}
\end{itemize}


\subsubsection{Example}
\begin{code}{latex} 
\begin{verbatim}
    \define{marie}{cool}
    \title{My Website}
    \begin{document}
        \section{Chapter One}
        \subsection{Whoarewe}
        \begin{paragraph}
            \textbf{Marie Curie!} \\
            \textit{An association for students of Physics!}
        \end{paragraph}
        \subsubsection{Code!}
            \begin{code}
                    We love tabs in code!
            \end{code}       
        \ref{NotDefinedLabel}
    \end{document} 
\end{verbatim} 
\end{code}

After rendering this results in: \\
    \title{My Website}
        \section{Chapter One}
        \subsection{Whoarewe}
        \begin{paragraph}
            \textbf{Marie Curie!} \\
            \textit{An association for students of Physics!}
        \end{paragraph}
        \subsubsection{Code!}
            \begin{code}
                    We love tabs in code!
            \end{code}       
        \ref{NotDefinedLabel}
